Mixture distribution data generation

### 2022-01-20 Ch3_samplesize/Datagen_viz.Rmd
Making the mixed distribution with parameters from the PP lnorm data in Ch2

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
#knitr::opts_chunk$set(fig.width=12, fig.height=6)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```

@@

```{r}
meanlogs <- c(3.011376, 2.670338, 2.842328, 2.830963, 1.637819, 2.351636, 2.117476)
sdlogs <- c(1.343584, 1.114171, 1.032824, 1.010781, 1.487352, 1.139045, 1.150798)

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
knitr::opts_chunk$set(fig.width=6, fig.height=4)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```

@@

```{r fig.height=12, fig.width=12}
meanlogs <- c(3.011376, 2.670338, 2.842328, 2.830963, 1.637819, 2.351636, 2.117476)
sdlogs <- c(1.343584, 1.114171, 1.032824, 1.010781, 1.487352, 1.139045, 1.150798)

samepis <- 1/7
pis <- rep(samepis, 7)

samp.size <- 50000
all.samples <- rep(0,samp.size)
for(i in 1:samp.size){

  which.group <- sample(1:7, size=1, replace=TRUE, prob=pis)
  all.samples[i] <- rlnorm(n=1,mean=meanlogs[which.group], sd=sdlogs[which.group])
}

@@

hist(all.samples, main= paste0("Sample"))
